%-------------------------
% Resume in Latex
% Author : Zeshui Song (Based on template by Jake Gutierrez)
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Zeshui Song} \\ \vspace{1pt}
    \small (929) 410-2239 $|$ \href{mailto:zeshui.song@cooper.edu}{\underline{zeshui.song@cooper.edu}} $|$ 
    \href{https://zeshui-song.github.io/}{\underline{zeshui-song.github.io}} $|$
    \href{https://www.linkedin.com/in/zeshui-song/}{\underline{linkedin.com/in/zeshui-song}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The Cooper Union for the Advancement of Science and Art}{New York, NY}
      {B.E. in Mechanical Engineering}{Aug. 2024 -- Present}
      \resumeItemListStart
        \resumeItem{\textbf{Relevant Coursework}: Statics, Dynamics, Mechanics of Materials, Materials Science, Design and Prototyping, Systems Engineering, Thermodynamics, Physics I-III, Calculus I-III}
      \resumeItemListEnd
    \resumeSubheading
      {Brooklyn Technical High School}{Brooklyn, NY}
      {Advanced Regents Diploma; AP Scholar with Distinction}{2020 -- 2024}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE / RESEARCH-----------
\section{Experience \& Research}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Tow Tank Research}{July 2025 -- Present}
      {Mechanical Designer}{New York, NY}
      \resumeItemListStart
        \resumeItem{Engineered a linear gantry using a NEMA 23 stepper, timing belt, and dual MGN12 rails for precise wing force measurement.}
        \resumeItem{Designed high-stiffness modular 80/20 framing to optimize load paths and minimize structural vibration.}
        \resumeItem{Integrated Arduino motion control with a TB6600 driver and limit switches for repeatable homing.}
      \resumeItemListEnd

    \resumeSubheading
      {Vertically Actuated Immersion Tank}{July 2025 -- Present}
      {Mechanical Designer}{New York, NY}
      \resumeItemListStart
        \resumeItem{Designed a NEMA 17/lead screw vertical actuator to study beetle behavior during air-to-water transitions.}
        \resumeItem{Developed motion control using GRBL and G-code to vary immersion rates and depth systematically.}
        \resumeItem{Optimized stability via an optical breadboard base and precision linear motion guide shafts.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{FSAE Suspension Dynamics Model} $|$ \emph{Python (SciPy), ODE, Kinematics}}{Nov. 2025 -- Dec. 2025}
          \resumeItemListStart
             \resumeItem{Characterized the front suspension of a Cooper Union FSAE car by developing a four-bar linkage kinematic model and solving for rigid-body static equilibrium.}

            \resumeItem{Derived a nonlinear effective spring constant and integrated it into a second-order ODE to simulate free oscillation, validating results against experimental video tracking data.}

            \resumeItem{Implemented geometric solvers using circle-circle intersections to ensure numerical robustness across the full range of motion.} 
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Wales: Water-Based Motion Rectifier} $|$ \emph{Onshape CAD, 3D Printing, Fluid Systems}}{Jan. 2025 -- May. 2025}
          \resumeItemListStart
            \resumeItem{Designed an Archimedes screw energy-buffer system in Onshape to decouple variable input for constant output.}
            \resumeItem{Developed a bevel gear transmission and crowned pulley system in Onshape to ensure reliable power transfer and self-centering of drive belts.}
            \resumeItem{Achieved a nearly constant output speed ($R^2 = 1.00$) by maintaining constant pressure in the upper reservoir via an overflow outlet.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{GigaSniffer: Spoilage Detector} $|$ \emph{Arduino, Sensor Calibration, Prototyping}}{Sept. 2024 -- Dec. 2024}
          \resumeItemListStart
            \resumeItem{Built a portable CO2 and ethanol sensor array using Arduino with rolling-average filtering for spoilage detection.}
            \resumeItem{Fabricated a laser-cut sensing chamber and integrated real-time graphical feedback for alerts.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{HX711 Digital Scale} $|$ \emph{Mechanical Design, Arduino, Signal Conditioning}}{April 2025 -- May 2025}
          \resumeItemListStart
            \resumeItem{Designed a 2000g scale with high linearity ($R^2 = 1.0$) using a pulley-based mechanism to isolate non-normal forces.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{CAD/Mechanical}{: Onshape, Solidworks, AutoCAD, Fusion 360, Inventor, 80/20 Aluminum Framing} \\
     \textbf{Prototyping/Fab}{: 3D Printing (FDM), Laser Cutting, Sand Casting, Soldering} \\
     \textbf{Programming}{: Python (SciPy, NumPy), MATLAB, Arduino IDE, C, GRBL} \\
     \textbf{Tools/Hardware}{: Arduino Microcontrollers, Stepper Motors (NEMA 17/23), TB6600 Motor Drivers, Load Cells (HX711), Gas Sensors (CO2, Ethanol)}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}